The Name of the Title is Hope

### 2020-03-19 methods.tex
Added trials subsection

>>>>

\subsection{Trials}
We had two variants.
%
The control version of the tool only showed programs that matched a type signature.
%
The treatment version showed three input-output examples with each program
suggested by the synthesizer.

Each participant went through one training task and four trial tasks.
%
The task was to find the best implementation of a type signature and a
description of what the program should do.
%
Timing began as soon as they were handed a card containing the task, and ended
when they pointed out the correct solution.
%
There was one correct answer per task---and task 3 had no correct solution.
%
Each participant was in a single variant for the entirety of their tasks.
